Data Preparation

### 2019-01-10 Data Preparation.Rmd
debugging corpus of manuals

### Courses
(In this section we use: `d_course`- contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.)

Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. For this we create the following three tibbles:
1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
Then we use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
d_ILO_detail <- d_ILO %>% 
  select(Code, ILO) %>%
  distinct() %>%
  count(Code) %>%
  rename(n_ILO = n)

@@

rm(n_catalogue, calendar_years, course_code, content_to_exclude,
   n, cat, pages_to_exclude, first_three_letters, first_pages_overview, page_start_loop, page_end_loop,
   page, current_page, following_page, current_page_content, following_page_content,
   course_overview, Code, year)
print(d_description)
```

@@

#### Tidy Text Format
We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
```{r tidy d_description}
d_overview_tidy <- d_description %>%
  select(Code, `Calendar Year`, Overview) %>%
  unnest_tokens(output = word, input = Overview)
print(d_overview_tidy)

d_description_tidy <- d_description %>%
  select(Code, `Calendar Year`, Description) %>%
  unnest_tokens(output = word, input = Description)
print(d_description_tidy)
```

@@

dictionary <- d_overview_tidy %>% 
  select(word) %>%
  distinct %>%
  arrange(word) %>%
  mutate(word_stem = purrr::map_chr(.x = word,
                                    .f = stem_hunspell))

@@

```{r stemming d_description}
d_overview_stem <- d_overview_tidy %>%
  left_join(dictionary, by = "word") %>%
  rename(word_original = word,
         word = word_stem) %>%
  filter(!word %in% stop_words$word)
print(d_overview_stem) # See humanities - humanity

d_description_stem <- d_description_tidy %>%
  left_join(dictionary, by = "word") %>%
  rename(word_original = word,
         word = word_stem) %>%
  filter(!word %in% stop_words$word)
print(d_description_stem) # See starting - start
```

### Course Manual 
We create a dataframe from the Corpus:
```{r}
manuals_td <- tidy(corpus_manuals)
```

@@

```{r}
manuals_tokens <- manuals_td %>%
  select(id,text) %>%
  mutate(Concentration= substring(id, 1, 3), Code= substring(id,1,7))%>%
  unnest_tokens(word, text)
```
####(Optional) Pre-processing Course Manuals- Removing stopwords
Some characters appear with sufficient frequency to be relevant but not often enough accross all courses to be deleted when using tf-idf (see sections bellow), it is therefore convenient to add some stopwords and remove numbers. For this we import stop_words from tidytext, and search all our words with grep for stand alone numbers. We save these words in different dataframes and then exclude with an antijoin.
```{r}

@@

my_stop_words <- data.frame (word = c(1:11, "students", "______________________________________________________________________________")) #no stemming ("students")
number_stopwords <- number_stopwords <- manuals_tokens %>% #can be cleaner by using unique (?)
  mutate(is_number=grepl("^[-]{0,1}[0-9]{0,}.{0,1}[0-9]{1,}$",word))%>% #finds stand alone numbers (incl. -, and .)
  filter(is_number==T)

>>>>

### Courses
Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. The tibble `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains; `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers; `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. We use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
d_ILO_detail <- d_ILO %>% 
  select(Code, ILO) %>%
  distinct() %>%
  count(Code) %>%
  rename(n_ILO = n)

@@

rm(corpus_catalogues,
   n_catalogue, calendar_years, course_code, content_to_exclude,
   n, cat, pages_to_exclude, first_three_letters, first_pages_overview, page_start_loop, page_end_loop,
   page, current_page, following_page, current_page_content, following_page_content,
   course_overview, Code, year)
print(d_description)
```

@@

#### Tidy Text Format
We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
```{r tidy d_description}
d_overview <- d_description %>%
  select(Code, `Calendar Year`, Overview) %>%
  unnest_tokens(output = word, input = Overview)
print(d_overview_tidy)

d_description <- d_description %>%
  select(Code, `Calendar Year`, Description) %>%
  unnest_tokens(output = word, input = Description)
print(d_description_tidy)
```

@@

dictionary <- d_overview %>% 
  select(word) %>%
  distinct %>%
  arrange(word) %>%
  mutate(word_stem = purrr::map_chr(.x = word,
                                    .f = stem_hunspell))

@@

```{r stemming d_description}
d_overview <- d_overview %>%
  left_join(dictionary, by = "word") %>%
  rename(word_original = word,
         word = word_stem) %>%
  filter(!word %in% stop_words$word)

d_description <- d_description %>%
  left_join(dictionary, by = "word") %>%
  rename(word_original = word,
         word = word_stem) %>%
  filter(!word %in% stop_words$word)

rm(stems, stem_hunspell)
print(d_overview_stem) # See humanities - humanity
```

### Course Manual 
We create a dataframe from the Corpus:
```{r d_manual}
d_manual <- tidy(corpus_manuals) %>%
  select(id, text) %>%
  mutate(Code = substring(id, 1, 7)) %>%
  select(-id) %>%
  rename(Manual = text)

rm(corpus_manuals)
print(d_manual)
```

```{r join manuals to d_course}
d_course <- full_join(d_course, d_manual, by = "Code")
```

@@

```{r d_manual tidy}
d_manual <- unnest_tokens(d_manual, output = word, input = Manual)
```

####(Optional) Pre-processing Course Manuals- Removing stopwords
Some characters appear with sufficient frequency to be relevant but not often enough accross all courses to be deleted when using tf-idf (see sections bellow), it is therefore convenient to add some stopwords and remove numbers. For this we import stop_words from tidytext, and search all our words with grep for stand alone numbers. We save these words in different dataframes and then exclude with an antijoin.
```{r}

my_sw <- c("______________________________________________________________________________")

@@

my_stop_words <- data.frame (word = c(1:11, "students", )) #no stemming ("students")
